---
title: "classification, regression with outlier exclusion"
author: "Steven"
date: "2024-02-16"
output:
  word_document: default
  html_document: default
  pdf_document: default
Source: "https://www.kaggle.com/datasets/anthonypino/melbourne-housing-market"
Reason for outlier elimination: problem for linear regression models, although they
  could be valuable to analyze under other situations
---


## Data source and original descriptions
<!--
Some Key Details
Suburb: Suburb

Address: Address

Rooms: Number of rooms

Price: Price in Australian dollars

Method:
S - property sold;
SP - property sold prior;
PI - property passed in;
PN - sold prior not disclosed;
SN - sold not disclosed;
NB - no bid;
VB - vendor bid;
W - withdrawn prior to auction;
SA - sold after auction;
SS - sold after auction price not disclosed.
N/A - price or highest bid not available.

Type:
br - bedroom(s);
h - house,cottage,villa, semi,terrace;
u - unit, duplex;
t - townhouse;
dev site - development site;
o res - other residential.

SellerG: Real Estate Agent

Date: Date sold

Distance: Distance from CBD in Kilometres

Regionname: General Region (West, North West, North, North east …etc)
Propertycount: Number of properties that exist in the suburb.

Bedroom2 : Scraped # of Bedrooms (from different source)

Bathroom: Number of Bathrooms

Car: Number of carspots

Landsize: Land Size in Metres

BuildingArea: Building Size in Metres

YearBuilt: Year the house was built

CouncilArea: Governing council for the area

Lattitude: Self explanitory

Longtitude: Self explanitory
-->


## Step 1: Data Cleaning and Preparation


```{r Step 1: Data Cleaning and Preparation}

# Load necessary libraries
library(dplyr)
library(readr)

# Step 1: Load the dataset

data_1 <- read_csv(file.choose())  # select the file interactively

# Step 2: Correct typos in column names
names(data_1)[names(data_1) == "Lattitude"] <- "Latitude"
names(data_1)[names(data_1) == "Longtitude"] <- "Longitude"

# Step 3: Calculate features
# Convert 'Date' from character to Date type. 

data_1$Date <- as.Date(data_1$Date, format = "%d/%m/%Y")

# Extract the year from the 'Date' column
data_1$YearOfSale <- as.numeric(format(data_1$Date, "%Y"))

# Calculate 'YearsSinceBuilt' and 'Priceperbuildingarea'
data_1$YearsSinceBuilt <- data_1$YearOfSale - data_1$YearBuilt
data_1$Priceperbuildingarea <- with(data_1, Price / BuildingArea)

# Step 4: Clean the data (Eliminate `NA` and `Inf` values)
data_1 <- na.omit(data_1) # Remove rows with NA values

#Identify numeric columns
numeric_cols <- sapply(data_1, is.numeric)

# Apply is.infinite only to numeric columns and then reduce to rows with any Inf values
rows_with_inf <- apply(data_1[, numeric_cols], 1, function(x) any(is.infinite(x)))

# Remove rows with Inf values
data_1 <- data_1[!rows_with_inf, ]

# hist 1
hist(data_1$Priceperbuildingarea)

# Step 5: Apply log transformation to 'Priceperbuildingarea'
data_1 <- data_1 %>%
  mutate(LogPriceperbuildingarea = log(Priceperbuildingarea + 1)) # Adding 1 to avoid log(0)

# hist 2 using the transformed data
hist(data_1$LogPriceperbuildingarea, main = "Histogram of Log(Priceperbuildingarea)", xlab = "Log(Priceperbuildingarea)")


```


```{r}
# Using names() function
column_names <- names(data_1)
print(column_names)

```
```{r}
# Identify numeric columns
numeric_columns <- sapply(data_1, is.numeric)

# Select only numeric columns
selected_data <- data_1[, numeric_columns]

# Calculate correlation matrix
correlation_matrix <- cor(selected_data, use = "pairwise.complete.obs")

# Print correlation matrix
print(correlation_matrix)
```


```{r}
# Load the corrplot package
library(corrplot)

# Calculate the correlation matrix
correlation_matrix <- cor(selected_data, use = "pairwise.complete.obs")

# Create the colored correlation grid
corrplot(correlation_matrix, method = "color")

```


```{r}


```

## Step 2: Classification with K-Means Clustering:

```{r Step 2: Classification with K-Means Clustering}
library(dplyr)
library(ggplot2)
library(cluster) # For clustering

# 'data_1' has been loaded and contains 'Longitude' and 'Latitude'
coords <- data_1 %>% select(Longitude, Latitude)

# Determine the optimal number of clusters (optional, for illustration)
# This step can be computationally intensive for large datasets
wss <- (nrow(coords)-1)*sum(apply(coords,2,var))
for (i in 2:15) wss[i] <- sum(kmeans(coords, centers=i)$withinss)
plot(1:15, wss, type="b", xlab="Number of Clusters", ylab="Within groups sum of squares")

# K-Means Clustering
set.seed(123) # For reproducibility
k <- 4 # Choose based on analysis, e.g., using the Elbow Method above
km_res <- kmeans(coords, centers = k)

# Assign class numbers to the original data and factorize
data_1$Class <- km_res$cluster
data_1$Class <- factor(data_1$Class)

# Step 4: Visualize on a Map
library(ggmap)
library(ggplot2)

# Basic plot with ggplot2
ggplot(data_1, aes(x = Longitude, y = Latitude, color = factor(Class))) +
  geom_point(alpha = 0.5) +
  labs(title = "Spatial Clustering of Data Points", color = "Class") +
  theme_minimal()


```

## Step 3: visualize histograms:
```{r Step 3: visualize histograms}
library(ggplot2)
library(dplyr)

# 'data_1' contains 'Y_label' and 'Class' columns
# Loop through each class and plot a histogram
unique_classes <- unique(data_1$Class)

# Create a list to store plots
plot_list <- list()

for(class in unique_classes) {
  plot <- data_1 %>%
    filter(Class == class) %>%
    ggplot(aes(x = LogPriceperbuildingarea)) +
    geom_histogram(bins = 30, fill = "skyblue", color = "black") +
    ggtitle(paste("Histogram of Priceperbuildingarea for Class", class)) +
    xlab("Y_label Value") +
    ylab("Frequency")
  
  print(plot) # Display the plot
  plot_list[[as.character(class)]] <- plot # Store the plot in a list 
}



```

## Step 4: Box plots
```{r Step 4: Box plots}
library(ggplot2)

# Total Box Plot for 'LogPriceperbuildingarea'
ggplot(data_1, aes(y = LogPriceperbuildingarea)) +
  geom_boxplot(fill = "lightblue", color = "darkblue") +
  ggtitle("Total Box Plot of Price per Building Area") +
  ylab("Price per Building Area") +
  xlab("")

# Box Plots for 'LogPriceperbuildingarea' by Class
ggplot(data_1, aes(x = factor(Class), y = LogPriceperbuildingarea, fill = factor(Class))) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Pastel1") +  # Color scheme
  ggtitle("Box Plot of Price per Building Area by Class") +
  xlab("Class") +
  ylab("Price per Building Area") +
  theme_light() +
  theme(legend.title = element_blank()) # Remove the legend title


```




## Step 5: Visualization of Price distribution

```{r Step 5: Visualization of Results}
library(ggplot2)
library(ggmap)

# PricePerBuildingArea, visualize classification based on it
ggplot(data_1, aes(x = Longitude, y = Latitude, color = LogPriceperbuildingarea)) + geom_point() + theme_minimal() + ggtitle("Price per Building Area Distribution")


```

## Step 6: Split Data into Training and Testing

```{r}
library(caret)
set.seed(123) # For reproducibility
index <- createDataPartition(data_1$LogPriceperbuildingarea, p = 0.8, list = FALSE)
trainData_1 <- data_1[index, ]
testData_1 <- data_1[-index, ]

trainData_trimmed_1 <- subset(trainData_1, select = c(Class, YearsSinceBuilt, LogPriceperbuildingarea))
#trainData_trimmed$Class <- factor(trainData_trimmed$Class)

testData_trimmed_1 <- subset(testData_1, select = c(Class, YearsSinceBuilt, LogPriceperbuildingarea))
#testData_trimmed$Class <- factor(testData_trimmed$Class)



```


```{r}
# Convert the columns to numeric
selected_data <- data_1[, c("Class", "YearsSinceBuilt", "LogPriceperbuildingarea")]
selected_data <- sapply(selected_data, as.numeric)

# Check if there are any missing values
if (anyNA(selected_data)) {
  # Handle missing values as needed
  selected_data <- na.omit(selected_data)
}

# Calculate the correlation matrix
correlation_matrix <- cor(selected_data, use = "pairwise.complete.obs")

# Create the colored correlation grid
corrplot(correlation_matrix, method = "color")


```

## Step 7: Run Regression
```{r}

model_1<- lm(LogPriceperbuildingarea ~ ., data = trainData_trimmed_1)
summary(model_1)
```
```{r}

```


```{r QQ and residual}
# Load necessary libraries
library(ggplot2)

# Extract residuals and fitted values
residuals_1 <- residuals(model_1)
fitted_values_1 <- fitted(model_1)

# Create a data frame
data_df_1 <- data.frame(residuals_1 = residuals_1, fitted_values_1 = fitted_values_1)

# QQ Plot
qqplot <- ggplot(data.frame(residuals_1 = residuals_1), aes(sample = residuals_1)) +
  geom_qq() +
  geom_qq_line() +
  ggtitle("QQ Plot of Residuals") +
  theme_minimal()

# Residual Plot
residual_plot <- ggplot(data_df_1, aes(x = fitted_values_1, y = residuals_1)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  ggtitle("Residual Plot") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_minimal()

# Show plots
print(qqplot)
print(residual_plot)

```

## Step 8: Show Algorithm Metrics

```{r}

predictions_1 <- predict(model_1, testData_trimmed_1)
actual_1 <- testData_trimmed_1$Priceperbuildingarea

# Calculate RMSE and MAE
RMSE_1 <- sqrt(mean((predictions_1 - actual_1) ^ 2))
MAE_1 <- mean(abs(predictions_1 - actual_1))

# Print metrics
print(paste("RMSE:", RMSE_1))
print(paste("MAE:", MAE_1))

```
## refine the model by introducing distance from center
## Step 9: calculate geo center
```{r}
data_2=data_1

# Calculate the center point
center_longitude <- mean(data_2$Longitude)
center_latitude <- mean(data_2$Latitude)
# Print the center point
cat("Center Longitude:", center_longitude, "\n")
cat("Center Latitude:", center_latitude, "\n")
```
## Step 10: calculate distance
```{r}
# Function to calculate distance between two points given their longitude and latitude
haversine_distance <- function(lon1, lat1, lon2, lat2) {
  # Convert latitude and longitude from degrees to radians
  lon1 <- lon1 * pi / 180
  lat1 <- lat1 * pi / 180
  lon2 <- lon2 * pi / 180
  lat2 <- lat2 * pi / 180
  
  # Haversine formula
  dlon <- lon2 - lon1
  dlat <- lat2 - lat1
  a <- sin(dlat/2)^2 + cos(lat1) * cos(lat2) * sin(dlon/2)^2
  c <- 2 * asin(sqrt(a))
  
  # Radius of the Earth in kilometers
  R <- 6371
  
  # Calculate the distance
  distance <- R * c
  return(distance)
}

# Calculate the center point
center_longitude <- mean(data_2$Longitude)
center_latitude <- mean(data_2$Latitude)
# Print the center point
cat("Center Longitude:", center_longitude, "\n")
cat("Center Latitude:", center_latitude, "\n")

# Calculate distance from center for each data point
data_2$distance_from_center <- apply(data_2, 1, function(row) {
  haversine_distance(as.numeric(row["Longitude"]), as.numeric(row["Latitude"]), center_longitude, center_latitude)
})

# Print the updated data frame
print(data_2)
```

## Step 11: Split Data into Training and Testing

```{r}
library(caret)
set.seed(123) # For reproducibility
index <- createDataPartition(data_2$LogPriceperbuildingarea, p=0.8, list=FALSE)
trainData_2 <- data_2[index, ]
testData_2 <- data_2[-index, ]

trainData_trimmed_2=subset(trainData_2, select = c(distance_from_center, YearsSinceBuilt, LogPriceperbuildingarea))
#trainData_trimmed$Class <- factor(trainData_trimmed$Class)

testData_trimmed_2=subset(testData_2, select = c(distance_from_center, YearsSinceBuilt, LogPriceperbuildingarea))
#testData_trimmed$Class <- factor(testData_trimed$Class)


```



## Step 12: Run Regression
```{r}

model_2 <- lm(LogPriceperbuildingarea ~ ., data = trainData_trimmed_2)
summary(model_2)
```
```{r}
# Extract residuals and fitted values for model2
residuals_2 <- residuals(model_2)
fitted_values_2 <- fitted(model_2)

# Create a data frame for model2
data_df_model_2 <- data.frame(residuals_2 = residuals_2, fitted_values_2 = fitted_values_2)

# QQ Plot for model2
qqplot_model <- ggplot(data.frame(residuals_2 = residuals_2), aes(sample = residuals_2)) +
  geom_qq() +
  geom_qq_line() +
  ggtitle("QQ Plot of Residuals - Model 2") +
  theme_minimal()

# Residual Plot for model2
residual_plot_model <- ggplot(data_df_model_2, aes(x = fitted_values_2, y = residuals_2)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  ggtitle("Residual Plot - Model 2") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_minimal()

# Show plots for model1
print(qqplot_model)
print(residual_plot_model)

```

## Step 13: visual comparison of both models
```{r}
# Predicted vs Actual values for model 1(distance based model)
plot(trainData_trimmed_1$LogPriceperbuildingarea, predict(model_1), 
     xlab = "Actual LogPriceperbuildingarea", ylab = "Predicted LogPriceperbuildingarea",
     main = "Model 1: Predicted vs Actual")

# Add a reference line with slope = 1
abline(0, 1, col = "red")

# Predicted vs Actual values for model 2(class based model)
plot(trainData_trimmed_2$LogPriceperbuildingarea, predict(model_2), 
     xlab = "Actual LogPriceperbuildingarea", ylab = "Predicted LogPriceperbuildingarea",
     main = "Model 2: Predicted vs Actual")

# Add a reference line with slope = 1
abline(0, 1, col = "red")
```

```{r}
# Set up the plotting area
par(mfrow = c(1, 2))

# Predicted vs Actual values for model 1(distance based model)
plot(trainData_trimmed_1$LogPriceperbuildingarea, predict(model_1), 
     xlab = "Actual LogPriceperbuildingarea", ylab = "Predicted LogPriceperbuildingarea",
     main = "Model 1: Predicted vs Actual")
abline(0, 1, col = "red")  # Add a reference line with slope = 1

# Predicted vs Actual values for model 2(class based model)
plot(trainData_trimmed_2$LogPriceperbuildingarea, predict(model_2), 
     xlab = "Actual LogPriceperbuildingarea", ylab = "Predicted LogPriceperbuildingarea",
     main = "Model 2: Predicted vs Actual")
abline(0, 1, col = "red")  # Add a reference line with slope = 1
```


```{r}
# Combine data frames for both models
combined_data <- rbind(
  data.frame(Model = "Model_1", residuals = residuals_1, fitted_values = fitted_values_1),
  data.frame(Model = "Model_2", residuals = residuals_2, fitted_values = fitted_values_2)
)

# QQ Plot
qqplot_combined <- ggplot(combined_data, aes(sample = residuals, color = Model)) +
  geom_qq() +
  geom_qq_line() +
  ggtitle("QQ Plot of Residuals") +
  theme_minimal()

# Residual Plot
residual_plot_combined <- ggplot(combined_data, aes(x = fitted_values, y = residuals, color = Model)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  ggtitle("Residual Plot") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_minimal()

# Show combined plots
print(qqplot_combined)
print(residual_plot_combined)

```
```{r}
# Calculate lower and upper bounds for residuals (e.g., 95% confidence interval)
lower_bound <- quantile(combined_data$residuals, 0.025)
upper_bound <- quantile(combined_data$residuals, 0.975)

# Residual Plot with bounds
residual_plot_combined <- ggplot(combined_data, aes(x = fitted_values, y = residuals, color = Model)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  geom_hline(yintercept = lower_bound, linetype = "dashed", color = "blue") +
  geom_hline(yintercept = upper_bound, linetype = "dashed", color = "blue") +
  ggtitle("Residual Plot with Bounds") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_minimal()

# Show the residual plot with bounds
print(residual_plot_combined)
```

```{r}
library(gridExtra)

# Calculate lower and upper bounds for residuals (e.g., 95% confidence interval)
lower_bound <- quantile(combined_data$residuals, 0.025)
upper_bound <- quantile(combined_data$residuals, 0.975)

# QQ Plot for Model 1
qqplot_model1 <- ggplot(combined_data[combined_data$Model == "Model_1", ], aes(sample = residuals)) +
  geom_qq() +
  geom_qq_line() +
  ggtitle("Model 1: QQ Plot of Residuals") +
  theme_minimal()

# Residual Plot for Model 1
residual_plot_model1 <- ggplot(combined_data[combined_data$Model == "Model_1", ], aes(x = fitted_values, y = residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  geom_hline(yintercept = lower_bound, linetype = "dashed", color = "blue") +
  geom_hline(yintercept = upper_bound, linetype = "dashed", color = "blue") +
  ggtitle("Model 1: Residual Plot") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_minimal()

# QQ Plot for Model 2
qqplot_model2 <- ggplot(combined_data[combined_data$Model == "Model_2", ], aes(sample = residuals)) +
  geom_qq() +
  geom_qq_line() +
  ggtitle("Model 2: QQ Plot of Residuals") +
  theme_minimal()

# Residual Plot for Model 2
residual_plot_model2 <- ggplot(combined_data[combined_data$Model == "Model_2", ], aes(x = fitted_values, y = residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  geom_hline(yintercept = lower_bound, linetype = "dashed", color = "blue") +
  geom_hline(yintercept = upper_bound, linetype = "dashed", color = "blue") +
  ggtitle("Model 2: Residual Plot") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_minimal()

# Arrange plots in a 2x2 grid
grid.arrange(qqplot_model1, residual_plot_model1, qqplot_model2, residual_plot_model2, ncol = 2, nrow = 2)

```
```{r}



```

## Step 14: Comparison of metrics

```{r}
summary(model_1)
summary(model_2)

# Metrics for model 1
metrics_model_1 <- summary(model_1)
r_squared_model_1 <- metrics_model_1$r.squared
adj_r_squared_model_1 <- metrics_model_1$adj.r.squared
residual_std_error_model_1 <- sqrt(metrics_model_1$sigma^2)
f_statistic_model_1 <- metrics_model_1$fstatistic[1]

# Metrics for model 2
metrics_model_2 <- summary(model_2)
r_squared_model_2 <- metrics_model_2$r.squared
adj_r_squared_model_2 <- metrics_model_2$adj.r.squared
residual_std_error_model_2 <- sqrt(metrics_model_2$sigma^2)
f_statistic_model_2 <- metrics_model_2$fstatistic[1]

# Print metrics for both models
cat("Model 1 Metrics:\n")
cat("R-squared:", r_squared_model_1, "\n")
cat("Adjusted R-squared:", adj_r_squared_model_1, "\n")
cat("Residual Standard Error:", residual_std_error_model_1, "\n")
cat("F-statistic:", f_statistic_model_1, "\n\n")

cat("Model 2 Metrics:\n")
cat("R-squared:", r_squared_model_2, "\n")
cat("Adjusted R-squared:", adj_r_squared_model_2, "\n")
cat("Residual Standard Error:", residual_std_error_model_2, "\n")
cat("F-statistic:", f_statistic_model_2, "\n")

```

## Step 15: Final comment

<!--
Model 1 (trainData_trimmed_1):
Variables: The independent variables include Class2, Class3, Class4, and YearsSinceBuilt. It seems like Class is a categorical variable that has been one-hot encoded into separate binary variables for each class.
Residuals: The range of residuals is quite wide, from -2.8777 to 6.5075, indicating some variation in the model's predictions compared to actual values.
Coefficients: All coefficients are statistically significant (p-value < 2e-16), indicating a strong association with the dependent variable. YearsSinceBuilt shows a positive correlation, suggesting that as the years since a building was built increase, so does the log price per building area.
R-squared: 0.2201, suggesting that approximately 22.01% of the variability in the log price per building area is explained by the model.
F-statistic: 498.7 with a p-value < 2.2e-16, suggesting the model is statistically significant overall.
Model 2 (trainData_trimmed_2):
Variables: This model includes distance_from_center and YearsSinceBuilt as independent variables.
Residuals: Similar to Model 1, there's a broad range, but slightly narrower, from -2.7966 to 6.3809.
Coefficients: Again, all variables are statistically significant. Unlike Model 1, distance_from_center shows a negative correlation with the dependent variable, indicating that as the distance from the center increases, the log price per building area decreases.
R-squared: 0.2934, which is higher than Model 1, indicating this model explains approximately 29.34% of the variability in the log price per building area.
F-statistic: Significantly higher than in Model 1 at 1468, with a p-value < 2.2e-16, indicating that the model is highly statistically significant.
Comparison:
Performance: Model 2 has a higher R-squared value (29.34% vs. 22.01%), indicating it provides a better fit to the data compared to Model 1.
Variables Impact: The inclusion of distance_from_center in Model 2 seems to have a significant impact on the price, suggesting that location relative to the center is an important factor in determining the price per building area.
Residual Standard Error (RSE): Model 2 has a lower RSE (0.4416) compared to Model 1 (0.464), which indicates that Model 2's predictions are, on average, closer to the actual values.
F-statistic: The F-statistic is much higher in Model 2, further supporting its greater explanatory power compared to Model 1.
Conclusion:
Based on the R-squared, residual standard error, and F-statistic, Model 2 appears to be the more effective model for predicting the log price per building area, likely due to the inclusion of the distance_from_center variable, which seems to be an important factor in explaining the variability in building area prices.
-->

## Step 16: Business application
<!--
Based on the analysis of the regression models and their respective metrics, here are some insights and recommendations that a real estate agent could consider:

Location Impact: The analysis shows that the distance_from_center significantly affects property prices. Real estate agents should emphasize properties closer to the center as they tend to have higher value. They could also use this information to help clients looking for investment opportunities to identify areas where real estate might appreciate faster.

Age of the Property: Both models highlight the importance of YearsSinceBuilt. Newly built or more recently constructed properties tend to fetch higher prices. Agents should stress the value of newer constructions in their marketing materials and when advising clients on selling prices or investment.

Property Class: In the first model, different classes of properties (Class2, Class3, Class4) significantly impact the price. This information can help agents tailor their sales strategies based on the property class and advise clients on which types of properties are more in demand or valuable.

Market Analysis: The substantial difference in R-squared values between the two models suggests that adding more relevant variables (like distance_from_center) can significantly improve understanding of market dynamics. Real estate agents should consider a wide range of factors when assessing property values and market trends.

Client Counseling: Agents can use insights from these models to counsel clients on pricing strategies and investment decisions. For sellers, emphasizing the benefits of location, recent renovations, or specific property classes can help justify higher asking prices. For buyers, understanding these factors can guide them to make better offers and investment decisions.

Marketing Strategies: Based on the significance of location and property age, agents might focus their marketing efforts on highlighting these features in property listings, especially for properties closer to city centers or newer constructions.

Investment Advice: The negative coefficient for distance_from_center in the second model suggests that proximity to the city center is highly valued. Agents could advise clients looking to invest in real estate to consider properties closer to the center as they might offer better returns.

Future Predictions: Agents can use these regression models to predict future price trends based on changes in the independent variables. This can be particularly useful for advising clients looking to buy or sell in the near future.

Robustness and Outliers: Given the insights on the importance of robust statistical methods, agents should be aware that outliers and unusual data points can significantly affect analysis. They should be prepared to reevaluate properties that don't fit general trends and provide contextual information to clients.

Continuous Learning and Adaptation: The real estate market is dynamic, and factors influencing prices can change. Agents should continuously update their knowledge and adapt their strategies based on the latest market data and statistical analyses.

These insights can help real estate agents provide more accurate advice, price properties more effectively, and develop targeted marketing strategies that resonate with potential buyers and sellers.
-->
