---
title: "classification, regression with outlier exclusion"
author: "Steven"
date: "2024-02-16"
output:
  word_document: default
  html_document: default
Source: "https://www.kaggle.com/datasets/anthonypino/melbourne-housing-market"
Reason for outlier elimination: problem for linear regression models, although they
  could be valuable to analyze under other situations
---


## Data source and original descriptions
<!--
Some Key Details
Suburb: Suburb

Address: Address

Rooms: Number of rooms

Price: Price in Australian dollars

Method:
S - property sold;
SP - property sold prior;
PI - property passed in;
PN - sold prior not disclosed;
SN - sold not disclosed;
NB - no bid;
VB - vendor bid;
W - withdrawn prior to auction;
SA - sold after auction;
SS - sold after auction price not disclosed.
N/A - price or highest bid not available.

Type:
br - bedroom(s);
h - house,cottage,villa, semi,terrace;
u - unit, duplex;
t - townhouse;
dev site - development site;
o res - other residential.

SellerG: Real Estate Agent

Date: Date sold

Distance: Distance from CBD in Kilometres

Regionname: General Region (West, North West, North, North east …etc)
Propertycount: Number of properties that exist in the suburb.

Bedroom2 : Scraped # of Bedrooms (from different source)

Bathroom: Number of Bathrooms

Car: Number of carspots

Landsize: Land Size in Metres

BuildingArea: Building Size in Metres

YearBuilt: Year the house was built

CouncilArea: Governing council for the area

Lattitude: Self explanitory

Longtitude: Self explanitory
-->


## Step 1: Data Cleaning and Preparation


```{r Step 1: Data Cleaning and Preparation}

# Load necessary libraries
library(dplyr)
library(readr)

# Step 1: Load the dataset

data_1 <- read_csv(file.choose())  # select the file interactively

# Step 2: Correct typos in column names
names(data_1)[names(data_1) == "Lattitude"] <- "Latitude"
names(data_1)[names(data_1) == "Longtitude"] <- "Longitude"

# Step 3: Calculate features
# Convert 'Date' from character to Date type. 

data_1$Date <- as.Date(data_1$Date, format = "%d/%m/%Y")

# Extract the year from the 'Date' column
data_1$YearOfSale <- as.numeric(format(data_1$Date, "%Y"))

# Calculate 'YearsSinceBuilt' and 'Priceperbuildingarea'
data_1$YearsSinceBuilt <- data_1$YearOfSale - data_1$YearBuilt
data_1$Priceperbuildingarea <- with(data_1, Price / BuildingArea)

# Step 4: Clean the data (Eliminate `NA` and `Inf` values)
data_1 <- na.omit(data_1) # Remove rows with NA values

#Identify numeric columns
numeric_cols <- sapply(data_1, is.numeric)

# Apply is.infinite only to numeric columns and then reduce to rows with any Inf values
rows_with_inf <- apply(data_1[, numeric_cols], 1, function(x) any(is.infinite(x)))

# Remove rows with Inf values
data_1 <- data_1[!rows_with_inf, ]

# hist 1
hist(data_1$Priceperbuildingarea)

# Step 5: Eliminate outliers in 'Priceperbuildingarea'
Q1 <- quantile(data_1$Priceperbuildingarea, 0.25, na.rm = TRUE)
Q3 <- quantile(data_1$Priceperbuildingarea, 0.75, na.rm = TRUE)
IQR <- Q3 - Q1
data_1 <- data_1 %>%
  filter(Priceperbuildingarea >= (Q1 - 1.5 * IQR) & Priceperbuildingarea <= (Q3 + 1.5 * IQR))

# hist 2
hist(data_1$Priceperbuildingarea)


```


```{r}
# Using names() function
column_names <- names(data_1)
print(column_names)

```
```{r}
# Identify numeric columns
numeric_columns <- sapply(data_1, is.numeric)

# Select only numeric columns
selected_data <- data_1[, numeric_columns]

# Calculate correlation matrix
correlation_matrix <- cor(selected_data, use = "pairwise.complete.obs")

# Print correlation matrix
print(correlation_matrix)
```


```{r}
# Load the corrplot package
library(corrplot)

# Calculate the correlation matrix
correlation_matrix <- cor(selected_data, use = "pairwise.complete.obs")

# Create the colored correlation grid
corrplot(correlation_matrix, method = "color")

```


```{r}


```

## Step 2: Classification with K-Means Clustering:

```{r Step 2: Classification with K-Means Clustering}
library(dplyr)
library(ggplot2)
library(cluster) # For clustering

# coordinates
coords <- data_1 %>% select(Longitude, Latitude)

# Determine the optimal number of clusters (optional, for illustration)
# This step can be computationally intensive for large datasets
wss <- (nrow(coords)-1)*sum(apply(coords,2,var))
for (i in 2:15) wss[i] <- sum(kmeans(coords, centers=i)$withinss)
plot(1:15, wss, type="b", xlab="Number of Clusters", ylab="Within groups sum of squares")

# K-Means Clustering
set.seed(123) # For reproducibility
k <- 4 # Choose based on analysis, e.g., using the Elbow Method above
km_res <- kmeans(coords, centers = k)

# Assign class numbers to the original data and factorize
data_1$Class <- km_res$cluster
data_1$Class <- factor(data_1$Class)

# Step 4: Visualize on a Map
library(ggmap)
library(ggplot2)

# Basic plot with ggplot2
ggplot(data_1, aes(x = Longitude, y = Latitude, color = factor(Class))) +
  geom_point(alpha = 0.5) +
  labs(title = "Spatial Clustering of Data Points", color = "Class") +
  theme_minimal()


```

## Step 3: visualize histograms:
```{r Step 3: visualize histograms}
library(ggplot2)
library(dplyr)

# 'data_1' contains 'Y_label' and 'Class' columns
# Loop through each class and plot a histogram
unique_classes <- unique(data_1$Class)

# Create a list to store plots 
plot_list <- list()

for(class in unique_classes) {
  plot <- data_1 %>%
    filter(Class == class) %>%
    ggplot(aes(x = Priceperbuildingarea)) +
    geom_histogram(bins = 30, fill = "skyblue", color = "black") +
    ggtitle(paste("Histogram of Priceperbuildingarea for Class", class)) +
    xlab("Y_label Value") +
    ylab("Frequency")
  
  print(plot) # Display the plot
  plot_list[[as.character(class)]] <- plot # Store the plot in a list 
}



```

## Step 4: Box plots
```{r Step 4: Box plots}
library(ggplot2)

# Total Box Plot for 'Priceperbuildingarea'
ggplot(data_1, aes(y = Priceperbuildingarea)) +
  geom_boxplot(fill = "lightblue", color = "darkblue") +
  ggtitle("Total Box Plot of Price per Building Area") +
  ylab("Price per Building Area") +
  xlab("")

# Box Plots for 'Priceperbuildingarea' by Class
ggplot(data_1, aes(x = factor(Class), y = Priceperbuildingarea, fill = factor(Class))) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Pastel1") +  # Color scheme
  ggtitle("Box Plot of Price per Building Area by Class") +
  xlab("Class") +
  ylab("Price per Building Area") +
  theme_light() +
  theme(legend.title = element_blank()) # Remove the legend title


```




## Step 5: Visualization of Price distribution

```{r Step 5: Visualization of Results}
library(ggplot2)
library(ggmap)

# PricePerBuildingArea, visualize classification based on it
ggplot(data_1, aes(x = Longitude, y = Latitude, color = Priceperbuildingarea)) + geom_point() + theme_minimal() + ggtitle("Price per Building Area Distribution")


```

## Step 6: Split Data into Training and Testing

```{r}
library(caret)
set.seed(123) # For reproducibility
index <- createDataPartition(data_1$Priceperbuildingarea, p = 0.8, list = FALSE)
trainData_1 <- data_1[index, ]
testData_1 <- data_1[-index, ]

trainData_trimmed_1 <- subset(trainData_1, select = c(Class, YearsSinceBuilt, Priceperbuildingarea))
#trainData_trimmed$Class <- factor(trainData_trimmed$Class)

testData_trimmed_1 <- subset(testData_1, select = c(Class, YearsSinceBuilt, Priceperbuildingarea))
#testData_trimmed$Class <- factor(testData_trimmed$Class)



```


```{r}
# Convert the columns to numeric
selected_data <- data_1[, c("Class", "YearsSinceBuilt", "Priceperbuildingarea")]
selected_data <- sapply(selected_data, as.numeric)

# Check if there are any missing values
if (anyNA(selected_data)) {
  # Handle missing values as needed
  selected_data <- na.omit(selected_data)
}

# Calculate the correlation matrix
correlation_matrix <- cor(selected_data, use = "pairwise.complete.obs")

# Create the colored correlation grid
corrplot(correlation_matrix, method = "color")


```

## Step 7: Run Regression
```{r}

model_1<- lm(Priceperbuildingarea ~ ., data = trainData_trimmed_1)
summary(model_1)
```
```{r}

```


```{r QQ and residual}
# Load necessary libraries
library(ggplot2)

# Extract residuals and fitted values
residuals_1 <- residuals(model_1)
fitted_values_1 <- fitted(model_1)

# Create a data frame
data_df_1 <- data.frame(residuals_1 = residuals_1, fitted_values_1 = fitted_values_1)

# QQ Plot
qqplot <- ggplot(data.frame(residuals_1 = residuals_1), aes(sample = residuals_1)) +
  geom_qq() +
  geom_qq_line() +
  ggtitle("QQ Plot of Residuals") +
  theme_minimal()

# Residual Plot
residual_plot <- ggplot(data_df_1, aes(x = fitted_values_1, y = residuals_1)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  ggtitle("Residual Plot") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_minimal()

# Show plots
print(qqplot)
print(residual_plot)

```

## Step 8: Show Algorithm Metrics

```{r}

predictions_1 <- predict(model_1, testData_trimmed_1)
actual_1 <- testData_trimmed_1$Priceperbuildingarea

# Calculate RMSE and MAE
RMSE_1 <- sqrt(mean((predictions_1 - actual_1) ^ 2))
MAE_1 <- mean(abs(predictions_1 - actual_1))

# Print metrics
print(paste("RMSE:", RMSE_1))
print(paste("MAE:", MAE_1))

```
## refine the model by introducing distance from center
## Step 9: calculate geo center
```{r}
data_2=data_1

# Calculate the center point
center_longitude <- mean(data_2$Longitude)
center_latitude <- mean(data_2$Latitude)
# Print the center point
cat("Center Longitude:", center_longitude, "\n")
cat("Center Latitude:", center_latitude, "\n")
```
## Step 10: calculate distance
```{r}
# Function to calculate distance between two points given their longitude and latitude
haversine_distance <- function(lon1, lat1, lon2, lat2) {
  # Convert latitude and longitude from degrees to radians
  lon1 <- lon1 * pi / 180
  lat1 <- lat1 * pi / 180
  lon2 <- lon2 * pi / 180
  lat2 <- lat2 * pi / 180
  
  # Haversine formula
  dlon <- lon2 - lon1
  dlat <- lat2 - lat1
  a <- sin(dlat/2)^2 + cos(lat1) * cos(lat2) * sin(dlon/2)^2
  c <- 2 * asin(sqrt(a))
  
  # Radius of the Earth in kilometers
  R <- 6371
  
  # Calculate the distance
  distance <- R * c
  return(distance)
}

# Calculate the center point
center_longitude <- mean(data_2$Longitude)
center_latitude <- mean(data_2$Latitude)
# Print the center point
cat("Center Longitude:", center_longitude, "\n")
cat("Center Latitude:", center_latitude, "\n")

# Calculate distance from center for each data point
data_2$distance_from_center <- apply(data_2, 1, function(row) {
  haversine_distance(as.numeric(row["Longitude"]), as.numeric(row["Latitude"]), center_longitude, center_latitude)
})

# Print the updated data frame
print(data_2)
```

## Step 11: Split Data into Training and Testing

```{r}
library(caret)
set.seed(123) # For reproducibility
index <- createDataPartition(data_2$Priceperbuildingarea, p=0.8, list=FALSE)
trainData_2 <- data_2[index, ]
testData_2 <- data_2[-index, ]

trainData_trimmed_2=subset(trainData_2, select = c(distance_from_center, YearsSinceBuilt, Priceperbuildingarea))
#trainData_trimmed$Class <- factor(trainData_trimmed$Class)

testData_trimmed_2=subset(testData_2, select = c(distance_from_center, YearsSinceBuilt, Priceperbuildingarea))
#testData_trimmed$Class <- factor(testData_trimed$Class)


```



## Step 12: Run Regression
```{r}

model_2 <- lm(Priceperbuildingarea ~ ., data = trainData_trimmed_2)
summary(model_2)
```
```{r}
# Extract residuals and fitted values for model2
residuals_2 <- residuals(model_2)
fitted_values_2 <- fitted(model_2)

# Create a data frame for model2
data_df_model_2 <- data.frame(residuals_2 = residuals_2, fitted_values_2 = fitted_values_2)

# QQ Plot for model2
qqplot_model <- ggplot(data.frame(residuals_2 = residuals_2), aes(sample = residuals_2)) +
  geom_qq() +
  geom_qq_line() +
  ggtitle("QQ Plot of Residuals - Model 2") +
  theme_minimal()

# Residual Plot for model2
residual_plot_model <- ggplot(data_df_model_2, aes(x = fitted_values_2, y = residuals_2)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  ggtitle("Residual Plot - Model 2") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_minimal()

# Show plots for model1
print(qqplot_model)
print(residual_plot_model)

```

## Step 13: visual comparison of both models
```{r}
# Predicted vs Actual values for model 1(distance based model)
plot(trainData_trimmed_1$Priceperbuildingarea, predict(model_1), 
     xlab = "Actual Priceperbuildingarea", ylab = "Predicted Priceperbuildingarea",
     main = "Model 1: Predicted vs Actual")

# Add a reference line with slope = 1
abline(0, 1, col = "red")

# Predicted vs Actual values for model 2(class based model)
plot(trainData_trimmed_2$Priceperbuildingarea, predict(model_2), 
     xlab = "Actual Priceperbuildingarea", ylab = "Predicted Priceperbuildingarea",
     main = "Model 2: Predicted vs Actual")

# Add a reference line with slope = 1
abline(0, 1, col = "red")
```

```{r}
# Set up the plotting area
par(mfrow = c(1, 2))

# Predicted vs Actual values for model 1(distance based model)
plot(trainData_trimmed_1$Priceperbuildingarea, predict(model_1), 
     xlab = "Actual Priceperbuildingarea", ylab = "Predicted Priceperbuildingarea",
     main = "Model 1: Predicted vs Actual")
abline(0, 1, col = "red")  # Add a reference line with slope = 1

# Predicted vs Actual values for model 2(class based model)
plot(trainData_trimmed_2$Priceperbuildingarea, predict(model_2), 
     xlab = "Actual Priceperbuildingarea", ylab = "Predicted Priceperbuildingarea",
     main = "Model 2: Predicted vs Actual")
abline(0, 1, col = "red")  # Add a reference line with slope = 1
```


```{r}
# Combine data frames for both models
combined_data <- rbind(
  data.frame(Model = "Model_1", residuals = residuals_1, fitted_values = fitted_values_1),
  data.frame(Model = "Model_2", residuals = residuals_2, fitted_values = fitted_values_2)
)

# QQ Plot
qqplot_combined <- ggplot(combined_data, aes(sample = residuals, color = Model)) +
  geom_qq() +
  geom_qq_line() +
  ggtitle("QQ Plot of Residuals") +
  theme_minimal()

# Residual Plot
residual_plot_combined <- ggplot(combined_data, aes(x = fitted_values, y = residuals, color = Model)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  ggtitle("Residual Plot") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_minimal()

# Show combined plots
print(qqplot_combined)
print(residual_plot_combined)

```
```{r}
# Calculate lower and upper bounds for residuals (e.g., 95% confidence interval)
lower_bound <- quantile(combined_data$residuals, 0.025)
upper_bound <- quantile(combined_data$residuals, 0.975)

# Residual Plot with bounds
residual_plot_combined <- ggplot(combined_data, aes(x = fitted_values, y = residuals, color = Model)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  geom_hline(yintercept = lower_bound, linetype = "dashed", color = "blue") +
  geom_hline(yintercept = upper_bound, linetype = "dashed", color = "blue") +
  ggtitle("Residual Plot with Bounds") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_minimal()

# Show the residual plot with bounds
print(residual_plot_combined)
```

```{r}
library(gridExtra)

# Calculate lower and upper bounds for residuals (e.g., 95% confidence interval)
lower_bound <- quantile(combined_data$residuals, 0.025)
upper_bound <- quantile(combined_data$residuals, 0.975)

# QQ Plot for Model 1
qqplot_model1 <- ggplot(combined_data[combined_data$Model == "Model_1", ], aes(sample = residuals)) +
  geom_qq() +
  geom_qq_line() +
  ggtitle("Model 1: QQ Plot of Residuals") +
  theme_minimal()

# Residual Plot for Model 1
residual_plot_model1 <- ggplot(combined_data[combined_data$Model == "Model_1", ], aes(x = fitted_values, y = residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  geom_hline(yintercept = lower_bound, linetype = "dashed", color = "blue") +
  geom_hline(yintercept = upper_bound, linetype = "dashed", color = "blue") +
  ggtitle("Model 1: Residual Plot") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_minimal()

# QQ Plot for Model 2
qqplot_model2 <- ggplot(combined_data[combined_data$Model == "Model_2", ], aes(sample = residuals)) +
  geom_qq() +
  geom_qq_line() +
  ggtitle("Model 2: QQ Plot of Residuals") +
  theme_minimal()

# Residual Plot for Model 2
residual_plot_model2 <- ggplot(combined_data[combined_data$Model == "Model_2", ], aes(x = fitted_values, y = residuals)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
  geom_hline(yintercept = lower_bound, linetype = "dashed", color = "blue") +
  geom_hline(yintercept = upper_bound, linetype = "dashed", color = "blue") +
  ggtitle("Model 2: Residual Plot") +
  xlab("Fitted Values") +
  ylab("Residuals") +
  theme_minimal()

# Arrange plots in a 2x2 grid
grid.arrange(qqplot_model1, residual_plot_model1, qqplot_model2, residual_plot_model2, ncol = 2, nrow = 2)

```
```{r}



```

## Step 14: Comparison of metrics

```{r}
summary(model_1)
summary(model_2)
# Metrics for model 1
metrics_model_1 <- summary(model_1)
r_squared_model_1 <- metrics_model_1$r.squared
adj_r_squared_model_1 <- metrics_model_1$adj.r.squared
residual_std_error_model_1 <- sqrt(metrics_model_1$sigma^2)
f_statistic_model_1 <- metrics_model_1$fstatistic[1]

# Metrics for model 2
metrics_model_2 <- summary(model_2)
r_squared_model_2 <- metrics_model_2$r.squared
adj_r_squared_model_2 <- metrics_model_2$adj.r.squared
residual_std_error_model_2 <- sqrt(metrics_model_2$sigma^2)
f_statistic_model_2 <- metrics_model_2$fstatistic[1]

# Print metrics for both models
cat("Model 1 Metrics:\n")
cat("R-squared:", r_squared_model_1, "\n")
cat("Adjusted R-squared:", adj_r_squared_model_1, "\n")
cat("Residual Standard Error:", residual_std_error_model_1, "\n")
cat("F-statistic:", f_statistic_model_1, "\n\n")

cat("Model 2 Metrics:\n")
cat("R-squared:", r_squared_model_2, "\n")
cat("Adjusted R-squared:", adj_r_squared_model_2, "\n")
cat("Residual Standard Error:", residual_std_error_model_2, "\n")
cat("F-statistic:", f_statistic_model_2, "\n")

```

## Step 15: Final comment

<!--
Certainly! Here's an explanation of the metrics for both Model 1 and Model 2:

### Model 1 Metrics:
- **R-squared (R²)**: This statistic measures the proportion of the variance in the dependent variable (Priceperbuildingarea) that is predictable from the independent variables (YearsSinceBuilt and distance_from_center). In Model 1, the R-squared value is approximately 0.441, indicating that about 44.1% of the variance in Priceperbuildingarea can be explained by the independent variables included in the model.

- **Adjusted R-squared**: This is the R-squared value adjusted for the number of predictors in the model. It penalizes the addition of unnecessary predictors that do not improve the model's explanatory power. In Model 1, the adjusted R-squared is approximately 0.441, which is very close to the R-squared value, indicating that the model is not penalized much for the inclusion of predictors.

- **Residual Standard Error (RSE)**: This statistic measures the average deviation of the observed values from the fitted values (predictions) in the units of the dependent variable (Priceperbuildingarea). In Model 1, the RSE is approximately 2069.569, suggesting that the typical difference between the observed and predicted values of Priceperbuildingarea is around 2069.569 units.

- **F-statistic**: This statistic tests the overall significance of the regression model by comparing the explained variance (due to regression) with the unexplained variance (residuals). In Model 1, the F-statistic is approximately 2693.406, with a very small p-value, indicating that the model is statistically significant.

### Model 2 Metrics:
- **R-squared (R²)**: In Model 2, the R-squared value is approximately 0.362, indicating that about 36.2% of the variance in Priceperbuildingarea can be explained by the independent variables included in the model.

- **Adjusted R-squared**: The adjusted R-squared in Model 2 is approximately 0.362, which is very close to the R-squared value.

- **Residual Standard Error (RSE)**: In Model 2, the RSE is approximately 2211.019, suggesting that the typical difference between the observed and predicted values of Priceperbuildingarea is around 2211.019 units.

- **F-statistic**: The F-statistic in Model 2 is approximately 968.9494, with a very small p-value, indicating that the model is statistically significant.

### Interpretation:
- Model 1 has a higher R-squared value and lower residual standard error compared to Model 2, indicating that Model 1 explains more of the variance in Priceperbuildingarea and has better predictive accuracy.
- Both models have statistically significant F-statistics, indicating that the regression models are overall significant.
- The inclusion of additional predictors (such as Class) in Model 2 did not lead to a substantial improvement in explanatory power, as evidenced by the slightly lower R-squared and adjusted R-squared values compared to Model 1.
-->

## Step 16: Business application
<!--
Based on the analysis of the regression models and their respective metrics, here are some insights and recommendations that a real estate agent could consider:

1. **Variable Importance**:
   - Both models indicate that the "YearsSinceBuilt" variable has a significant positive effect on the "Priceperbuildingarea." This suggests that newer buildings tend to have higher prices per building area.
   - Model 1 also includes "distance_from_center" as a significant predictor, indicating that proximity to the center is associated with higher prices per building area.

2. **Model Comparison**:
   - Model 1, which includes only "YearsSinceBuilt" and "distance_from_center," performs better in terms of R-squared value and residual standard error compared to Model 2, which additionally includes the "Class" variable.
   - The addition of the "Class" variable in Model 2 does not substantially improve the model's explanatory power, suggesting that it may not be a crucial factor in determining the price per building area.

3. **Recommendations**:
   - **Focus on Property Age and Location**: Real estate agents should emphasize the age of the property (YearsSinceBuilt) and its proximity to the city center (distance_from_center) when advising clients on pricing strategies.
   - **Consider Additional Factors Carefully**: While the "Class" variable is included in Model 2, its impact on the price per building area is not significant. Real estate agents should carefully evaluate the relevance and significance of additional factors before incorporating them into pricing models.

4. **Target Marketing Strategies**:
   - Agents could tailor their marketing strategies based on the characteristics highlighted by the models. For instance, they could highlight the age of newer properties or emphasize the proximity of properties to the city center in marketing materials.
   - They could also target specific demographics or segments of buyers who are likely to value these characteristics more, such as young professionals seeking modern properties or urban dwellers prioritizing convenience.

5. **Continuous Evaluation and Improvement**:
   - Real estate agents should continuously evaluate and refine their pricing models based on new data and market trends. They should monitor the performance of different variables and adjust their strategies accordingly to ensure optimal pricing accuracy and competitiveness in the market.

By leveraging the insights gained from the regression analysis, real estate agents can make more informed decisions when pricing properties and advising clients, ultimately enhancing their effectiveness and success in the real estate market.
-->
